Project Membach

### 2020-06-06 project.mems.Rmd
cleaner Membach Rmd code

```{r diffs/bc-d168-acf-pacf}
plot_grid(
  train.bc %>% diff(lag=168) %>%  acf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  train.bc %>% diff(lag=168) %>%  acf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  train.bc %>% diff(lag=168) %>% pacf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  train.bc %>% diff(lag=168) %>% pacf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  nrow = 2
)
```

```{r diffs/bc-d-d168-acf-pacf}
plot_grid(
  train.bc %>% diff() %>% diff(lag=168) %>%  acf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  train.bc %>% diff() %>% diff(lag=168) %>%  acf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  train.bc %>% diff() %>% diff(lag=168) %>% pacf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  train.bc %>% diff() %>% diff(lag=168) %>% pacf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous()
  ,
  nrow = 2
)
```

>>>>

```{r diffs/bc-d168-acf-pacf}
plot_grid(
  train.bc %>% diff(lag=168) %>%  acf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  train.bc %>% diff(lag=168) %>%  acf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  train.bc %>% diff(lag=168) %>% pacf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  train.bc %>% diff(lag=168) %>% pacf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  nrow = 2
)
```

```{r diffs/bc-d-d168-acf-pacf}
plot_grid(
  train.bc %>% diff() %>% diff(lag=168) %>%  acf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  train.bc %>% diff() %>% diff(lag=168) %>%  acf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  train.bc %>% diff() %>% diff(lag=168) %>% pacf(lag.max = 24,    plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  train.bc %>% diff() %>% diff(lag=168) %>% pacf(lag.max = 168*4, plot = F, na.action = na.pass) %>% autoplot() + labs(title = NULL) + scale_x_continuous(),
  nrow = 2
)
```
